---
title: "Update Food Groups"
filters:
  - sorting-hat
  - ripper
extensions:
  sorting-hat:
    keep:
      - r
    verbose: true
  ripper:
    include-yaml: false
    output-dir: "../pipeline"
    output-name: "update_food_groups"  
    script-links-position: "none"

format: gfm
---

In the second stage of the pipeline, we're
following the scripts and updating the food groups.

```{r}
#| sorting-hat: remove

# Load libraries
library(dplyr)
library(tidyr)
library(targets)
library(here)
devtools::load_all()

tar_load(
    c(mah_hh_total, 
    mah_meta, 
    food_groupings,
    new_groups,
    fish_enc_g),

    store = here("_targets")
)
```

```{r}
update_groups_targets <- list()
```

Keep general information and columns with the specific foods:

```{r}
#| sorting-hat: remove
mah_hh_total <- mah_hh_total %>%
  select(vh:all_foods_pc, agiv:zavok)
```

```{r}
update_groups_targets <- append(
  update_groups_targets,
  tar_target(
    mah_hh_total,
    command = {
      mah_hh_total <- mahery_files %>%
        str_subset("mah_hh_dietary_intake.csv") %>%
        read.csv() %>%
        tibble()
    }
  )
)
```

```{r}
# Convert food columns to a variable of 'var_names' and their corresponding 
# weight in grams (long format)
mah_hh_long <- mah_hh_total %>%  # (~28 million entries)
  pivot_longer(  
    cols = agiv:zavok,
    names_to = "var_names",
    values_to = "wt_g")
```
# Drop rows with no consumption recorded
mah_hh_long <- mah_hh_long %>%  # 370987 obs
  filter(wt_g != 0)
# Match foods to their full names
mah_foods <- mah_hh_long %>%
  left_join(mah_meta %>% 
              select(Variable, `Malagasy Name`),
            by = join_by(var_names == Variable)) %>%
  rename(FoodName_Recoded = `Malagasy Name`)
# If no name, use var_name as recoded name
mah_foods <- mah_foods %>% 
  mutate(FoodName_Recoded = case_when(is.na(FoodName_Recoded) ~ var_names, 
         .default = FoodName_Recoded))

### Merge and standardize recoded and translated names 
# Remove extra whitespace from FoodName_Recoded
mah_foods$FoodName_Recoded <- gsub("\\s+", " ", mah_foods$FoodName_Recoded)
mah_foods$FoodName_Recoded <- trimws(mah_foods$FoodName_Recoded)

# Join by FoodName_Recoded and get FoodName_Translated, Category, Subcategory
mah_foods <- mah_foods %>%
  left_join(new_groups, join_by(FoodName_Recoded), 
            relationship = "many-to-one", unmatched = "drop")

# Fix FoodName_Recoded values
mah_foods <- fix_recoded(diet_df = mah_foods)
# Fix FoodName_Translated values
mah_foods <- fix_trans(diet_df = mah_foods)
# Fix makoba for fish
mah_foods <- fix_makoba(diet_df = mah_foods)
# Extract and remove medicines 
temp <- fix_med(diet_df = mah_foods)
mah_foods <- temp$diet_df
mah_foods_med <- temp$med_df
# Extract and remove traditional medicines
temp <- fix_trad_med(diet_df = mah_foods)
mah_foods <- temp$diet_df
mah_foods_trad_med <- temp$trad_med_df
# Remove erroneous entries, tobacco, measure words, and misc
mah_foods <- fix_remove(diet_df = mah_foods)

### Fill in missing translations
# If FoodName_Translated is NA, see if can fill in
# Original translations, keeping only the first in each group
old_trans <- hh_comb_groups %>% 
  select(FoodName_Recoded, FoodName_Translated) %>%
  mutate(FoodName_Translated = na_if(FoodName_Translated, "")) %>%
  drop_na(FoodName_Translated) %>%
  distinct() %>%
  group_by(FoodName_Recoded) %>%
  filter(row_number() == 1)
# Fill in translations using old translations
mah_foods <- mah_foods %>%
  rows_patch(old_trans, by = "FoodName_Recoded", unmatched = "ignore")
# Fill in translations using fish encyclopedia
mah_foods <- mah_foods %>%
  rows_patch(fish_enc_g %>% select(FoodName_Recoded, Common.Name) %>%
               drop_na() %>% distinct() %>%
               rename(FoodName_Translated = Common.Name) %>%
               group_by(`FoodName_Recoded`) %>% 
               filter(row_number() == 1), 
             by = "FoodName_Recoded", unmatched = "ignore") %>%
  rows_patch(fish_enc_g %>% select(FoodName_Recoded, ComName) %>%
               drop_na() %>% distinct() %>%
               rename(FoodName_Translated = ComName) %>%
               group_by(`FoodName_Recoded`) %>% 
               filter(row_number() == 1), 
             by = "FoodName_Recoded", unmatched = "ignore") %>%
  rows_patch(fish_enc_g %>% select(FoodName_Recoded, Scientific.name) %>%
               drop_na() %>% distinct() %>%
               rename(FoodName_Translated = Scientific.name) %>%
               group_by(`FoodName_Recoded`) %>% 
               filter(row_number() == 1), 
             by = "FoodName_Recoded", unmatched = "ignore")

# Fill in any remaining missing categories 
mah_foods <- mah_foods %>%
  rows_patch(new_groups, by = "FoodName_Recoded", unmatched = "ignore") %>%
  rename(grams = wt_g) %>%
  # Add column indicating source of grams is from mahery weighted data
  mutate(grams_source = "mahery")

# Drop unnecessary columns and reorder columns
mah_hh_comb_groups <- mah_foods %>%
  mutate(project = "mahery", 
         region = 1,
         proj_reg_vill_hh = 
           paste0(project, "_", region, "_", village, "_", household),
         hh_size = base_people) %>%
  arrange(project, region, village, household, hh_size, proj_reg_vill_hh, 
          year, month, week, day, meal, FoodName_Recoded) %>%
  select(project, region, village, household, hh_size, proj_reg_vill_hh, 
         year, month, week, day, meal, FoodName_Recoded, FoodName_Translated, 
         Category, Subcategory, var_names, grams)

# Check all categories and food names are filled in
temp <- mah_hh_comb_groups[is.na(mah_hh_comb_groups$Category), ]
temp <- mah_hh_comb_groups[is.na(mah_hh_comb_groups$FoodName_Recoded), ]


# # Save MAHERY household consumption with new food groups
# write.csv(mah_hh_comb_groups,
#           paste0(wd, res_dir, "mah_hh_per_meal_grams_categs_long.csv"),
#           row.names = FALSE)

    # # Detection of outliers
    # mah_large_wt <- mah_hh_comb_groups %>%
    #   arrange(grams) %>%
    #   filter(grams > 2000)
    # write.csv(mah_large_wt, paste0(wd, "Cleaned_Data/MAHERY/Intermediate_Outputs/", 
    #                                "mah_large_wt.csv"))