---
title: "flat_register_inputs.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

# register_inputs

This is a simple function that registers the input data.

This project has a zipped dataset in inputs that we zipped
directly from the [old GitHub repo](https://github.com/MAHERY-Cohort-Data/madagascar_data_cleaning).
So, to get the necessary input files, we must open the zip file
and list its contents. The function `register_inputs()` will do this for us.

```{r}
library(here)
library(readr)
library(stringr)
library(dplyr)
```

```{r}
input_path <- here("data", "inputs", "01_gold_mine", "madagascar-cohort-data-zip/madagascar_data_cleaning-main.zip")
```

```{r}
unzip(input_path, list = TRUE)
```

For this subproject we're going to want to register only the files in
`Data/MAHERY`

```{r development-register_inputs}
# Prepare the code of your function here
```

```{r function-register_inputs}
#' register_inputs Title
#'
#' Description of the function
#' 
#' @param input_path path to the zipped dataset
#' @param regex regular expression to filter the files to be registered
#' @importFrom dplyr filter pull
#' @importFrom stringr str_detect
#' @return vector of file paths
#' @export
#'
#' @examples
register_inputs <- function(input_path, regex = "MAHERY") {
  
  # List the contents of the zip file
  contents <- unzip(input_path, list = TRUE)
  
  # Filter the contents based on the regex
  contents %>%
    filter(str_detect(Name, regex)) %>%
    pull(Name) %>%
    return()
  
}
```

```{r examples-register_inputs}
register_inputs(
  here(
    "data", 
    "inputs", 
    "01_gold_mine", 
    "madagascar-cohort-data-zip/madagascar_data_cleaning-main.zip"
    ),
  regex = "Data\\/MAHERY"
  )
```

Great! That can go into our pipeline as the starting point.

```{r tests-register_inputs}
test_that("register_inputs works", {
  expect_true(inherits(register_inputs, "function"))
})
```


```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_register_inputs.Rmd", vignette_name = "Register Inputs", check=FALSE, overwrite = TRUE, open_vignette = FALSE)
```

