---
title: "flat_register_inputs.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

# register_inputs

This is a simple function that registers the input data.

This project has a zipped dataset in inputs that we zipped
directly from the [old GitHub repo](https://github.com/MAHERY-Cohort-Data/madagascar_data_cleaning).
So, to get the necessary input files, we must open the zip file
and list its contents. The function `register_inputs()` will do this for us.

```{r}
library(here)
library(readr)
library(stringr)
library(dplyr)
```

```{r}
input_path <- here("data", "inputs", "01_gold_mine", "madagascar-cohort-data-zip/madagascar_data_cleaning-main.zip")
```

```{r}
unzip(input_path, list = TRUE)
```

For this subproject we're going to want to register only the files in
`Data/MAHERY`

```{r development-register_inputs}
# Prepare the code of your function here
```

```{r function-register_inputs}
#' List matching file paths from a zip archive
#'
#' Lists the contents of a zipped dataset and returns the paths of files
#' whose names match the supplied regular expression.
#' 
#' @param input_path path to the zipped dataset
#' @param regex regular expression to filter the files to be registered
#' @importFrom dplyr filter pull
#' @importFrom stringr str_detect
#' @return vector of file paths
#' @export
#'
#' @examples
register_inputs <- function(input_path, regex = "MAHERY") {
  
  # List the contents of the zip file
  contents <- unzip(input_path, list = TRUE)
  
  # Filter the contents based on the regex
  contents %>%
    filter(str_detect(Name, regex)) %>%
    pull(Name) %>%
    return()
  
}
```

```{r examples-register_inputs, eval=FALSE}
register_inputs(
  here(
    "data", 
    "inputs", 
    "01_gold_mine", 
    "madagascar-cohort-data-zip/madagascar_data_cleaning-main.zip"
    ),
  regex = "Data\\/MAHERY"
  )
```

Great! That can go into our pipeline as the starting point.

```{r tests-register_inputs}
test_that("register_inputs lists only matching files from input zip", {
  tmpdir <- withr::local_tempdir()

  files <- file.path(
    tmpdir,
    c(
      "raw/MAHERY_clinic_2024.csv",
      "raw/MAHERY_households_2024.csv",
      "raw/OTHER_site_2024.csv",
      "metadata/readme.txt"
    )
  )

  dir.create(dirname(files[1]), recursive = TRUE)
  dir.create(dirname(files[4]), recursive = TRUE)
  file.create(files)

  zip_path <- file.path(tmpdir, "incoming_dataset.zip")
  old_wd <- setwd(tmpdir)
  withr::defer(setwd(old_wd))

  zip(
    zipfile = zip_path,
    files = c(
      "raw/MAHERY_clinic_2024.csv",
      "raw/MAHERY_households_2024.csv",
      "raw/OTHER_site_2024.csv",
      "metadata/readme.txt"
    )
  )

  result <- register_inputs(zip_path, regex = "MAHERY")

  expect_equal(
    sort(result),
    sort(c(
      "raw/MAHERY_clinic_2024.csv",
      "raw/MAHERY_households_2024.csv"
    ))
  )
})
```

As an additional helper, we're defining an unzip tracker that will help
us keep track of files that we unzip.

```{r function-unzip_tracker}
#' Unzip selected files and return extracted paths
#'
#' Extracts matching files from a zip archive and returns the paths
#' of the extracted files for use in reproducible pipelines such as
#' `{targets}`.
#'
#' @param zipfile Path to zip archive.
#' @param files Character vector of internal zip paths to extract.
#' @param exdir Extraction directory.
#' @param junkpaths Should directory structure inside archive be discarded?
#' @param overwrite Should existing files be overwritten?
#'
#' @return Character vector of extracted file paths.
#'
#' @export
unzip_tracked <- function(
  zipfile,
  files,
  exdir,
  junkpaths = TRUE,
  overwrite = TRUE
) {

  info <- unzip(zipfile, list = TRUE)

  matched <- str_subset(info$Name, paste(files, collapse = "|"))

  out_files <- if (junkpaths) {
    file.path(exdir, basename(matched))
  } else {
    file.path(exdir, matched)
  }

  unzip(
    zipfile = zipfile,
    files = matched,
    exdir = exdir,
    junkpaths = junkpaths,
    overwrite = overwrite
  )

  out_files
}
```

```{r tests-unzip_tracked}
test_that("unzip_tracked returns extracted file paths", {

  skip_if_not_installed("zip")

  tmpdir <- tempdir()

  file_a <- file.path(tmpdir, "a.txt")
  writeLines("hello", file_a)

  zipfile <- file.path(tmpdir, "test.zip")

  zip::zipr(
    zipfile = zipfile,
    files = file_a
  )

  extracted <- unzip_tracked(
    zipfile = zipfile,
    files = "a.txt",
    exdir = file.path(tmpdir, "out")
  )

  expect_true(all(file.exists(extracted)))
  expect_equal(basename(extracted), "a.txt")
})
```


```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_register_inputs.Rmd", vignette_name = "Register Inputs", check=FALSE, overwrite = TRUE, open_vignette = FALSE)
```

