---
title: "Load MAHERY Data"
filters:
  - sorting-hat
  - ripper
extensions:
  sorting-hat:
    keep:
      - r
    verbose: true
  ripper:
    include-yaml: false
    output-dir: "../R"
    output-name: "load_data"  
    script-links-position: "none"

format: gfm
---

This is a simple notebook that documents the "load data" step.
The code chunks get exported to a script which is then
run as part of the pipeline by `bakepipe`.

```{r}
#| sorting-hat: keep
library(prospectorMahery)
library(bakepipe)
library(stringr)
library(here)
library(dplyr)
library(readr)
library(readxl)
```

Setting up directories now relies on the `here` package:

```{r}
#| sorting-hat: keep
wd <- here()
inputs_dir <- file.path(wd, "data", "inputs", "01_gold_mine", "madagascar-cohort-data-zip")
code_dir <- file.path(wd, "R")
results_dir <- file.path(wd, "data", "outputs")
```

To load in the data, we register the input file with `bakepipe`
by using the `external_in` function:

```{r}
#| sorting-hat: keep
repo_files <- register_inputs(
    file.path(inputs_dir, "madagascar_data_cleaning-main.zip"),
    regex = "Data\\/MAHERY"
  )
```

```{r}
#| sorting-hat: remove
repo_files
```

`bakepipe` only accepts string literals as inputs, so,
as a hack, we are using an equivalence test to ensure
the file exists before using it as an input to `bakepipe`
targets.

```{r}
#| sorting-hat: keep
target_file <- "mah_hh_dietary_intake.csv"
mah_hh_total_f <- repo_files %>%
    str_subset(target_file)

mah_hh_total_f %>%
    unzip(file.path(inputs_dir, "madagascar_data_cleaning-main.zip"), exdir = inputs_dir, files = ., junkpaths = TRUE)
infile <- file.path(inputs_dir, target_file)

if(!file.exists(infile)) {
    stop("File does not exist.")
}

if(infile != "/n/holylabs/cgolden_lab/Lab/frontier/works/prospectors/prospectorMahery/data/inputs/01_gold_mine/madagascar-cohort-data-zip/mah_hh_dietary_intake.csv") {
    stop("File path does not match expected path.")
}

mah_hh_total <- external_in("/n/holylabs/cgolden_lab/Lab/frontier/works/prospectors/prospectorMahery/data/inputs/01_gold_mine/madagascar-cohort-data-zip/mah_hh_dietary_intake.csv") %>%
    read_csv(.)
```

```{r}
#| sorting-hat: remove
mah_hh_total %>%
    summary()
```


