---
title: "MAHERY Pipeline"
format: gfm
engine: knitr
---

Here we document, create, and run the pipeline all in
one file thanks to Quarto and `targets`.

For the backend, we'll use this Quarto notebook as the 
"orchestrator," meaning that the pipeline runs any time
this notebook is executed/rendered. First, let's get 
the script files from the inputs directory:

```{r}
devtools::load_all()
```

```{r}
library(stringr)
library(dplyr)
library(here)
```

The inputs were provided by stagecoach. The manifest for
the stagecoach run is in `stagecoach_manifest.yaml` if you want to check it out.

```{r}
#| packages: [stringr, dplyr, here]
repo_files <- register_inputs(
  here(
    "data", 
    "inputs", 
    "01_gold_mine", 
    "madagascar-cohort-data-zip/madagascar_data_cleaning-main.zip"
    ),
  regex = ".+"
  ) %>%
  str_c(here("data", "inputs", "01_gold_mine", "madagascar-cohort-data-zip"), .)
```

It looks like MAHERY only has an individual cleaning script,
meaning we can turnover this project pretty quickly.

First, we unzip the data that is relevant to this pipeline:

```{r}
target_files <- c(
  "mah_hh_dietary_intake\\.csv",
  "mahery_metadata\\.xlsx",
  "MAHERY_DARWIN_ForMatching_AllUniqueFoods_to_Nutritional_Equivalents2025Feb1\\.xlsx",
  "dar_hh_weekly_per_month_grams_categs_long\\.csv",
  "fish_enc_17Feb2025\\.csv"
  )
```

```{r}
#| format: file

mahery_files <- unzip_tracked(
  here(
    "data", 
    "inputs", 
    "01_gold_mine", 
    "madagascar-cohort-data-zip/madagascar_data_cleaning-main.zip"
    ),
  files = target_files,
  junkpaths = TRUE,  
  exdir = here("data", "inputs", "01_gold_mine", "madagascar-cohort-data-zip/")
)
```

Now that that is done, the rest of the pipeline is found in each of the
respective QMD files; when each of those is rendered,
the code will be extracted to the `pipeline` directory and run as part of the pipeline.

