---
title: "MAHERY Pipeline"
filters:
  - sorting-hat
  - ripper
extensions:
  sorting-hat:
    keep:
      - r
    verbose: true
  ripper:
    include-yaml: false
    output-dir: "R"
    script-links-position: "none"

params:
  export: true
format: gfm
---

Here we document, create, and run the pipeline all in
one file thanks to Quarto and the [`bakepipe` package](https://vangberg.github.io/bakepipe/index.html).
`bakepipe` is a package by Harrry Vangberg that I stumbled across online,
built to facilitate simpler, more script-focused,
and less involved reproducible pipelines.
While it is driven by `targets` under the hood, it is
much more lightweight and is intended for ease of use
and simplicity — ideal for scenarios like this where you
have been given a batch of scripts and just want to 
run them in a pipeline without having to deliberately
refactor them into a more `targets`-like structure.

See [here](https://vangberg.github.io/bakepipe/index.html#motivation) for more info on `bakepipe`.


To set up a pipeline with `bakepipe`, you just need to have
a `_bakepipe.R` file in your project. This tells `bakepipe`
to scaffold all of the targets stuff in the background for you.
Then in each of your scripts, simply register (in a Make-like,
or even more familiar, snakemake-like way) the input and 
output files respectively. `bakepipe` will then figure out the 
dependencies and build the DAG for you.

Because it is so simple, `bakepipe` is ideal
for quick pipelines that are just IO, no fancy stuff.

For the backend, we'll use this Quarto notebook as the 
"orchestrator," meaning that the pipeline runs any time
this notebook is executed/rendered. First, let's get 
the script files from the inputs directory:

```{r}
devtools::load_all(".")
library(bakepipe)
library(stringr)
library(dplyr)
library(here)
```

The inputs were provided by stagecoach. The manifest for
the stagecoach run is in `stagecoach_manifest.yaml` if you want to check it out.

```{r}
repo_files <- register_inputs(
  here(
    "data", 
    "inputs", 
    "01_gold_mine", 
    "madagascar-cohort-data-zip/madagascar_data_cleaning-main.zip"
    ),
  regex = ".+"
  )
repo_files
```

It looks like MAHERY only has an individual cleaning script,
meaning we can turnover this project pretty quickly.

## Pipeline Run

```{r}
#| eval: false
library(bakepipe)
```

We can check the status of the pipeline with `bakepipe::status()`:

```{r}
#| eval: false
status()
```

First, we unzip the data that is relevant to this pipeline:

```{r}
target_files <- c(
  "mah_hh_dietary_intake\\.csv",
  "mahery_metadata\\.xlsx",
  "MAHERY_DARWIN_ForMatching_AllUniqueFoods_to_Nutritional_Equivalents2025Feb1\\.xlsx",
  "dar_hh_weekly_per_month_grams_categs_long\\.csv",
  "fish_enc_17Feb2025\\.csv"
  ) %>%
  paste(collapse = "|")
  
zip_paths <- repo_files %>%
  str_subset(target_files)

unzip(
  here(
    "data", 
    "inputs", 
    "01_gold_mine", 
    "madagascar-cohort-data-zip/madagascar_data_cleaning-main.zip"
    ),
  files = zip_paths,
  junkpaths = TRUE,  
  exdir = here("data", "inputs", "01_gold_mine", "madagascar-cohort-data-zip/")
)
```

```{r}
#| eval: false
status()
```

Finally, we run the pipeline with `bakepipe::run()`

```{r}
#| eval: false
run()
```
