---
subtitle: "DARWIN Household Total 1-week Fish Consumption"
filters:
  - sorting-hat
  - ripper
extensions:
  sorting-hat:
    keep:
      - r
    verbose: true
  ripper:
    include-yaml: false
    output-dir: "../../tests/testthat"
    output-name: "test-pipeline_node-03"
    script-links-position: "none"
format: gfm
---

At this stage, the purpose is to obtain total household 
1-week consumption of fish foods for DARWIN.
Total fish consumption is calculated using the fish recall, with the 
addition of certain fish captured using the weekly recall (see node (2)).

```{r}
#| deployment: main

#| sorting-hat: keep
library(dplyr)
library(readxl)
library(stringr)
library(here)
library(targets)
```

Load raw file paths, fish encyclopedia, which includes unique fish ids with taxonomic
information and weights obtained from CPUE and FishBase/SeaLifeBase:
  
```{r}
tar_load(
  c(mahery_files, dar_hh_weekly_with_grams, hh_fish),
  store = here("_targets")
)
```


```{r}
new_groups <- mahery_files %>%
  str_subset(
    "MAHERY_DARWIN_ForMatching_AllUniqueFoods_to_Nutritional_Equivalents2025Feb1"
  ) %>%
  read_xlsx(sheet = "ItemLevelMatches") %>%
  rename(FoodName_Recoded = `FoodName_Recoded NOT THE FINAL ONES - MUST GET`) %>%
  select(FoodName_Recoded, FoodName_Translated,
         Category, Subcategory) %>%
  mutate(FoodName_Recoded = str_replace(FoodName_Recoded, "cafe", "café"))

darwin_pop <- mahery_files %>%
  str_subset("darwin_pop") %>%
  read.csv()
```

<!-- Data processing goes here... -->

Final targets for this step:

```{r}
dar_hh_weekly_per_month_fish_grams_categs_long <- {
  x <- c(mahery_files, dar_hh_weekly_with_grams, hh_fish, darwin_pop, new_groups)
  tibble()
}
dar_hh_weekly_per_month_fish_wide <- {
  x <- c(mahery_files, dar_hh_weekly_with_grams, hh_fish, darwin_pop, new_groups)
  tibble()
}
```
