---
subtitle: "step 7"
filters:
  - sorting-hat
  - ripper
extensions:
  sorting-hat:
    keep:
      - r
    verbose: true
  # ripper:
  #   include-yaml: false
  #   output-dir: "../pipeline"
  #   output-name: "07_mah_a_load_data"
  #   script-links-position: "none"
format: gfm
---

# Read in data

First, we read in all of the libraries and functions

```{r}
#| sorting-hat: remove

library(dplyr)        # for tidy data routines #TODO slim this down
library(readxl)           # for reading excel files
library(stringr)
library(here)
library(purrr)             
devtools::load_all()
```

Load the `targets` store:

```{r}
#| sorting-hat: remove

library(targets)
tar_load(mahery_files, store = here("_targets"))
```

```{r}
mah_load_data_targets <- list()
```

Read in previously cleaned MAHERY total consumption data:

```{r}
#| sorting-hat: remove
mah_hh_total <- mahery_files %>%
  str_subset("mah_hh_dietary_intake.csv") %>%
  read.csv()

mah_hh_total
```

This would be better off as a tibble for convenience:

```{r}
#| sorting-hat: remove
mah_hh_total <- tibble(mah_hh_total)
```

```{r}
mah_load_data_targets <- append(
  mah_load_data_targets,
  tar_target(
    mah_hh_total,
    command = {
      mah_hh_total <- mahery_files %>%
        str_subset("mah_hh_dietary_intake.csv") %>%
        read.csv() %>%
        tibble()
    }
  )
)
```

Read in MAHERY metadata

```{r}
#| sorting-hat: remove
mah_meta <- mahery_files %>% 
  str_subset("mahery_metadata.xlsx") %>%
  read_excel(., sheet = 2)

mah_meta <- mah_meta %>%
  mutate(`Malagasy Name` = tolower(`Malagasy Name`))
```

Looks good, add it to the targets:

```{r}
mah_load_data_targets <- append(
  mah_load_data_targets,
  tar_target(
    mah_meta,
    command = {
      mah_meta <- mahery_files %>% 
        str_subset("mahery_metadata.xlsx") %>%
        read_excel(., sheet = 2) %>%
        mutate(`Malagasy Name` = tolower(`Malagasy Name`))
    }
  )
)
```

Read in updated food categories and subcategories for all distinct food items, 
downloaded from source: https://docs.google.com/spreadsheets/d/1etaxo9hN3kCNDqS5GDdMyYLA0vKJcqb3aqbciFXkLYs/edit?gid=0#gid=0
Note: older version of categorization was from "dar_mah_categs17Oct2023_CG.xlsx",
which can be found in Combined/Data/Old_Data

```{r}
#| sorting-hat: remove

new_groups <- mahery_files %>%
  str_subset(
    "MAHERY_DARWIN_ForMatching_AllUniqueFoods_to_Nutritional_Equivalents2025Feb1.xlsx"
    ) %>%
  read_xlsx(., sheet = "ItemLevelMatches")

new_groups <- new_groups %>% 
  rename(FoodName_Recoded = `FoodName_Recoded NOT THE FINAL ONES - MUST GET`) %>%
  select(FoodName_Recoded, FoodName_Translated,
         Category, Subcategory) %>%
  mutate(FoodName_Recoded = gsub("cafe", "café", FoodName_Recoded))
new_groups
```

Add to targets:
```{r}
mah_load_data_targets <- append(
  mah_load_data_targets,
  tar_target(
    new_groups,
    command = {
      mahery_files %>%
        str_subset(
          "MAHERY_DARWIN_ForMatching_AllUniqueFoods_to_Nutritional_Equivalents2025Feb1.xlsx"
        ) %>%
        read_xlsx(., sheet = "ItemLevelMatches") %>%
        rename(FoodName_Recoded = `FoodName_Recoded NOT THE FINAL ONES - MUST GET`) %>%
        select(FoodName_Recoded, FoodName_Translated,
               Category, Subcategory) %>%
        mutate(FoodName_Recoded = gsub("cafe", "café", FoodName_Recoded))
    }
  )
)
```
 
Read in DARWIN data with new food groupings

```{r}
#| sorting-hat: remove

hh_comb_groups <- mahery_files %>%
  str_subset("dar_hh_weekly_per_month_grams_categs_long.csv") %>%
  read.csv() %>%
  tibble()

hh_comb_groups
```

Add to targets:

```{r}
mah_load_data_targets <- append(
  mah_load_data_targets,
  tar_target(
    food_groupings,
    command = {
      hh_comb_groups <- mahery_files %>%
        str_subset("dar_hh_weekly_per_month_grams_categs_long.csv") %>%
        read.csv() %>%
        tibble()
    }
  )
)
```

